%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - BBR Partners %%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

BBR Partners

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Vice President, Portfolio \& Wealth Advisory position in Chicago. I should be upfront: my background is in academic finance, not wealth management. But the analytical core of this role---portfolio construction, asset allocation, and evaluating investment strategies across public and private markets---is what I've spent my career studying.

\vspace{6pt}

My published and ongoing research focuses on equity risk premia, factor models, derivatives valuation, and understanding what drives returns across asset classes. I've built quantitative frameworks for analyzing portfolio performance and risk, worked with large-scale financial datasets, and communicated technical results to demanding audiences at venues including the NBER and the Federal Reserve System. I code daily, have strong financial modeling skills, and I'm working through the CFA program (Level II passed), which satisfies your licensing requirement.

\vspace{6pt}

What draws me to BBR is the depth of investment thinking the advisory model demands. Serving sophisticated clients across the full range of portfolio and wealth considerations rewards the kind of rigorous, first-principles analysis I've built my career around. I'd welcome the chance to discuss how my background could contribute to the advisory team.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
