%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - The Brattle Group %%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

The Brattle Group

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Associate position (Economics Focus) in the Chicago office. Applying rigorous economic and financial analysis to high-stakes problems---litigation, regulation, corporate strategy---is exactly the kind of work where my background adds value.

\vspace{6pt}

I hold a Ph.D.\ in Finance from Arizona State University, with research focused on equity risk premia, derivatives valuation, and market microstructure. My work is published in the \textit{Journal of Political Economy} and has been presented at the NBER and Federal Reserve System. This background has given me deep experience framing quantitative research questions, building defensible empirical analyses, and communicating technical conclusions to skeptical audiences---skills that translate directly to expert consulting engagements. I'm proficient in statistical software, comfortable managing complex projects, and experienced in supervising research teams through my academic work.

\vspace{6pt}

I'd welcome the chance to discuss how my research background could contribute to Brattle's practice. A writing sample is available upon request.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
