%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - Curi Capital %%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

Curi Capital

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Senior Analyst -- Manager Research position on the Private Markets team in Chicago. Investment due diligence that spans public and private markets and requires both analytical depth and cross-functional collaboration is well-suited to my background.

\vspace{6pt}

I should be upfront: my background is in academia, not allocator or RIA settings. But evaluating investment strategies is the core of what I do. My research focuses on equity risk premia, factor models, and derivatives valuation---understanding what drives returns, separating skill from risk exposure, and assessing whether investment approaches hold up under scrutiny. I've built quantitative frameworks for analyzing strategy performance, worked with large-scale financial datasets across asset classes, and presented technical results to demanding audiences. I code daily, have strong analytical and financial modeling skills, and I'm working through the CFA program (Level II passed).

\vspace{6pt}

I'd welcome the chance to discuss how my research background could contribute to Curi Capital's manager research and investment process.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
