%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - DRW %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

DRW

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Equity Analyst -- Special Situations position within DRW's Equity teams. Prop trading firms that take research seriously are rare, and the scope of this role---real-time event analysis, financial modeling, and direct collaboration with traders---is a compelling match for what I do well.

\vspace{6pt}

I should be upfront: my background is in academia, not industry. But the overlap with this role is unusually direct. My published and ongoing research focuses on options-implied valuation and equity risk premia, which means I've spent years doing some version of what this role asks for: building models under uncertainty, constructing probability estimates from incomplete data, and working hands-on with large-scale financial datasets. I code daily, am fluent in equity and derivatives valuation from years of empirical and theoretical research, and I'm working through the CFA program (Level II passed) to round out my industry credentialing.

\vspace{6pt}

What draws me to this role specifically is the catalyst-driven, thesis-oriented nature of the work. Academic research is slow; I want to apply the same analytical rigor on a timeframe where the results actually move capital. I'd welcome the chance to discuss how my background fits what you're building on DRW's Equity desk.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
