%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - The Hartford %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

The Hartford

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Data Scientist Economist position in The Hartford's Global Insights Center. I see there is also a posting for a Senior Economist position. Developing economic views and building the quantitative models to support them go hand-in-hand in my opinion, so I'd be glad to discuss either role.

\vspace{6pt}

I should be upfront: my background is in academia, not industry. However, the core of what I do is general equilibrium thinking, rigorous quantitative analysis, and finding structure in problems where the obvious approaches fall short. My research has required extracting novel insights from messy financial data, developing econometric models that hold up to scrutiny, and explaining technical results to skeptical audiences. I'm also working through the CFA program (Level II passed) to strengthen my industry credentialing.

\vspace{6pt}

What caught my attention about these roles is the focus on developing economic indicators that actually inform business decisions---underwriting, strategy, client advisory. That's more applied than most of what I get to work on now, exactly the kind of problem where textbook methods might not get you very far, and where the ability to think from first principles matters.

\vspace{6pt}

I'd welcome the chance to discuss how my background could contribute to the Global Insights Center's work.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
