%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - IMC Trading %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

IMC Trading

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Quantitative Researcher -- Data Curation position in Chicago. The focus on US equity and equity options data, combined with the bridge between research pipelines and live trading, is a strong match for what I do.

\vspace{6pt}

My background is in academic finance rather than industry, but I've spent years doing the core work this role requires. I build and maintain research pipelines on exactly the data sources this position manages---CRSP/Compustat, TAQ tick-level data, and full-surface options data. That means integrating, cleaning, and validating large-scale financial datasets where accuracy matters and errors propagate. My published and ongoing research uses these pipelines to conduct statistical modeling on equity returns, options-implied signals, and market microstructure patterns. I code daily, am experienced with high-frequency and real-time data structures, and understand the data quality standards that quantitative trading demands.

\vspace{6pt}

I'd welcome the chance to discuss how my background could contribute to IMC's data and research infrastructure.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
