%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - Manulife / John Hancock %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

Manulife

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Small Cap Equity Investment Analyst position on your Chicago-based team. A concentrated group of sector specialists running real capital with a collaborative research culture is exactly the kind of environment where I want to work.

\vspace{6pt}

I should be upfront: my background is in academia, not industry. I haven't covered small-cap financials professionally. But the analytical core of what I do transfers directly---I build valuation models, assess risk-return tradeoffs, and extract conclusions from financial data where the signal is not obvious. My published and ongoing research focuses on equity risk premia, factor models, and derivatives valuation, all grounded in the same fundamental question this role asks every day: what is this security worth and why? I code daily, am comfortable modeling earnings and cash flows, and I'm working through the CFA program (Level II passed).

\vspace{6pt}

What draws me to this role is the depth of analysis it demands. Fundamental research on small-cap names rewards the kind of careful, first-principles thinking that I've built my career around. I'd welcome the chance to discuss how my background could contribute to the team's work.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
