%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - MetLife %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

MetLife Investment Management

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Director, Equity Research Analyst position in Chicago. I'll be direct: my background is in academic finance, not buy-side fundamental research. But the analytical foundation I bring---equity valuation, risk-return assessment, and rigorous empirical analysis---is the same foundation this role builds on.

\vspace{6pt}

My published and ongoing research focuses on understanding what drives equity returns: risk premia estimation, factor models, and the cross-section of expected returns. I've built valuation frameworks grounded in financial statement data, worked extensively with large-scale equity datasets, and presented technical results to demanding audiences at venues including the NBER and the Federal Reserve System. I code daily, am comfortable modeling earnings and cash flows, and I'm working through the CFA program (Level II passed).

\vspace{6pt}

What draws me to this role is the depth of fundamental coverage it demands. Actively tracking a concentrated set of names and developing investment theses rewards the kind of careful, first-principles analysis I've built my career around. I'd welcome the chance to discuss how my background could contribute to MetLife Investment Management's equity research.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
