%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - Optiver %%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

Optiver

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Quantitative Researcher position on the Systematic Volatility Trading team. An early-stage systematic vol effort at a firm with Optiver's infrastructure and market access is a rare opportunity, and it aligns closely with what I've spent the last several years researching.

\vspace{6pt}

I should be upfront: my background is in academia, not industry. But the substance of my research is directly relevant. I've published on the decomposition of equity risk premia using options-implied information, studied the variance risk premium as a return predictor, and built empirical frameworks for extracting signals from full options surfaces---all grounded in large-scale financial data. My work on algorithmic execution with institutional and high-frequency data also gives me a concrete perspective on how research translates into live trading. I code daily, am fluent in equity and derivatives valuation from years of empirical and theoretical research, and I'm working through the CFA program (Level II passed).

\vspace{6pt}

What appeals to me about this role is the chance to build something from the ground up. I'm looking to apply the analytical rigor I've developed in academia on problems where the results are measured in P\&L, not citations. I'd welcome the chance to discuss how my background fits what you're building on the SVT desk.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
