%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - PEAK6 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

PEAK6 Capital Management

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Quantitative Researcher -- Execution position. Analyzing and optimizing algorithmic execution is one of my active research areas, and doing that work at a proprietary options trading firm is a natural next step.

\vspace{6pt}

My background is in academic finance rather than industry, but the overlap here is specific. I have a current research paper studying how institutional trading algorithms route orders, access liquidity across venues, and impact prices---using high-frequency data to diagnose execution quality and algorithmic behavior. That work required building the statistical frameworks to measure performance against noisy microstructure data, exactly the analytical toolkit an execution QR needs. My broader research spans options-implied valuation, equity risk premia, and factor models, all grounded in large-scale financial datasets. I code daily and have a strong mathematical foundation in estimation, optimization, and time-series analysis.

\vspace{6pt}

I'd welcome the chance to discuss how my research background could contribute to PEAK6's execution strategies.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
