%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - Point72 %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

Point72

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Quantitative Researcher position on the Systematic Credit team, based in Chicago. A new team building systematic strategies from the ground up at a firm with Point72's resources is a compelling opportunity, and the research scope---alpha generation, risk modeling, and option pricing---maps closely to my background.

\vspace{6pt}

My background is in academic finance rather than industry, but the substance is directly relevant. My published and ongoing research focuses on developing and testing alpha signals, building factor and risk models, and pricing derivatives---grounded in large-scale financial data and rigorous statistical methods. I have deep experience with option pricing models, numerical optimization, and P\&L attribution through my work on equity risk premia decomposition. I code daily, build research and simulation pipelines from scratch, and have a strong foundation in the structural and statistical modeling this role requires.

\vspace{6pt}

My research has concentrated on equities and options rather than credit, but the quantitative toolkit---signal construction, risk factor estimation, model validation---transfers across asset classes. I also trade synthetically constructed duration-hedged credit spreads in my personal portfolio, so the asset class is not unfamiliar. I'd welcome the chance to discuss how my background could contribute to the team you're building.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
