%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - RSM US LLP %%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

RSM US LLP

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Valuation Services Manager position focused on complex financial instruments, based in Chicago. The technical core of this role---option pricing models, Monte Carlo simulation, and derivatives valuation---is exactly what my research background is built on.

\vspace{6pt}

I should be upfront: my background is in academia, not consulting. But the quantitative substance transfers directly. My published and ongoing research centers on derivatives valuation, including extracting risk-neutral information from option surfaces and modeling variance risk premia. I build Monte Carlo simulation frameworks, work with lattice and continuous-time pricing models, and have spent years developing the mathematical foundations behind the instruments this role values---convertibles, embedded derivatives, and complex equity-linked securities. I code daily in MATLAB, have strong Excel and financial modeling skills, and I'm working through the CFA program (Level II passed).

\vspace{6pt}

I'm also comfortable communicating technical results to non-technical audiences, which I understand is central to client-facing valuation work. I'd welcome the chance to discuss how my background could contribute to RSM's valuation practice.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
