%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - Simon, Dill & Associates %%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

Simon, Dill \& Associates

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Portfolio Management Analyst position. Supporting investment strategies and portfolio management with rigorous analytical work is a natural fit for my background, and I'm drawn to a firm where that work is connected directly to client outcomes.

\vspace{6pt}

I should be upfront: my background is in academia, not industry. But the overlap with this role is substantial. My research centers on exactly the problems that inform portfolio construction---risk premia estimation, factor models, and the quantitative foundations of modern portfolio theory. I've built Monte Carlo simulation frameworks, worked extensively with large-scale financial datasets, and developed reproducible analytical pipelines from the ground up. I code daily, have strong financial modeling skills, and I've passed CFA Level II.

\vspace{6pt}

I'm looking to apply these skills in a setting where the analysis supports real investment decisions for real clients. I'd welcome the chance to discuss how my background could contribute to your portfolio management team.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
