%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - Valkyrie Trading %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

Valkyrie Trading

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Quantitative Researcher position. Both the modeling and execution tracks align with my research---I work on options and volatility modeling on the one hand and algorithmic execution quality on the other. A successful trading strategy requires optimization on both fronts, and I appreciate that Valkyrie treats them as complementary.

\vspace{6pt}

My background is in academic finance rather than industry, but the substance is directly relevant. My published and ongoing research spans options-implied valuation, variance risk premia, and the decomposition of equity risk premia using full options surfaces---the quantitative foundations of volatility modeling and statistical position-taking. Separately, my work on algorithmic equities execution studies how trading algorithms route orders, access liquidity, and impact prices using high-frequency data, which connects directly to the execution track's focus on post-trade analysis and market microstructure. I code daily, build simulation and backtesting frameworks, and have a strong mathematical foundation in estimation, optimization, and time-series analysis.

\vspace{6pt}

I'd welcome the chance to discuss how my research background could contribute to Valkyrie's trading strategies.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
