%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - The Voleon Group %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

The Voleon Group

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Member of Research Staff position. A research role where the work spans from basic research to live trading---and where the team takes academic rigor seriously---is exactly what I'm looking for.

\vspace{6pt}

My background is in academic finance, where I've spent years working on the kinds of problems Voleon tackles: predicting equity returns, decomposing risk premia, and building models that hold up against noisy financial data. My published and ongoing research focuses on extracting signals from large-scale financial datasets---cross-sectional equity returns, high-frequency market data, full options surfaces---using econometric and statistical methods. I've built simulation frameworks, validated models against out-of-sample data, and developed reproducible research pipelines from the ground up. I code daily and have a strong mathematical foundation spanning estimation theory, optimization, and time-series analysis.

\vspace{6pt}

What draws me to Voleon is the emphasis on bridging research and production. I want to work where the models I build are tested by markets, not just referees. I'd welcome the chance to discuss how my background fits your research program.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
