%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - The Voleon Group (Trading) %%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

The Voleon Group

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Quantitative Trading Strategist Lead position in the Trading Operations group. I'll be direct: I don't have industry trading experience. But the research overlap with this role is unusually specific, and I wanted to make the case for a conversation.

\vspace{6pt}

My current research includes a paper on the anatomy of algorithmic equities execution---studying how institutional trading algorithms route orders, access liquidity, and impact prices using high-frequency data. That work required building the exact analytical toolkit this role demands: measuring execution quality across venues, diagnosing market-impact patterns, and developing statistical frameworks for evaluating algorithmic performance against noisy microstructure data. My broader research spans equity risk premia, factor models, and derivatives valuation, all grounded in large-scale financial datasets and rigorous statistical methods. I code daily and have a strong mathematical foundation in estimation, optimization, and time-series analysis.

\vspace{6pt}

If you're open to a candidate whose market microstructure expertise comes from the research side rather than a trading desk, I'd welcome the conversation.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
