%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Cover Letter - Zuckerman Investment Group %%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{color,hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% Commands
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header (matches resume)
\begin{center}
{\LARGE \textbf{Tyler Beason, Ph.D.}} \\[6pt]
Chicago metro, IL \quad $\bullet$ \quad 480-735-9791 \quad $\bullet$ \quad \email{tylerbeasonpublic@gmail.com} \quad $\bullet$ \quad \href{http://tbeason.com}{tbeason.com}
\end{center}

\vspace{20pt}

% Date
\today

\vspace{12pt}

Zuckerman Investment Group

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I'm applying for the Investment Analyst position at Zuckerman Investment Group. The combination of fundamental equity research and direct client engagement is exactly the kind of work I'm looking to do.

\vspace{6pt}

I should be upfront: my background is in academia, not industry. However, the core of what I do---rigorous quantitative analysis and finding structure in problems where the obvious approaches fall short---applies to applied investment research. My work centers on risk premia, alpha signals, and factor models; I've extracted insights from messy financial data and explained technical results to skeptical audiences. I'm published in the \textit{Journal of Political Economy} and working through the CFA program (Level II passed).

\vspace{6pt}

I can generate new ideas, I can conduct in-depth analysis and testing of those ideas, I can explain and defend those ideas, I can sell those ideas, and I can abandon those ideas when they are no longer working. If that is the kind of person you want in this role, please reach out.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Tyler Beason

\end{document}
